\EVOSUITE at the SBFT 2023 Tool Competition

### 2023-03-15 papers/sbst23/paper_sbst23.tex
Fine tune figures
Fix typo
Format long affiliation
WIP: results

\author{%
  \IEEEauthorblockN{Sebastian Schweikl}
  \IEEEauthorblockA{%
    \textit{University of Passau} \\
    Passau, Germany \\
    email address or ORCID
  }
  \and
  \IEEEauthorblockN{Gordon Fraser}
  \IEEEauthorblockA{%
    \textit{University of Passau} \\
    Passau, Germany \\
    email address or ORCID
  }
  \and
  \IEEEauthorblockN{Andrea Arcur}
  \IEEEauthorblockA{%
    \textit{Kristiania University College and Oslo Metropolitan University} \\
    Oslo, Norway \\
    email address or ORCID
  }
}

@@

%-------------------------------------------------------------------------
\section{Introduction}
%
For the last 10 years, the annual unit test generation competition has
evaluated progress on unit test generation tools using a benchmark of Java
classes, on which different tools are applied and compared. In the 2023 edition
of the competition, five tools were applied on a set of \cuts classes. Details
about the procedure of the competition, the technical framework, and the
benchmark classes can be found in the competition
report~\cite{SBST-toolcomp22}. \EVOSUITE achieved an overall score of \score,
which was the highest among the competing and baseline tools.

@@

%-------------------------------------------------------------------------
\section{Competition Setup}

@@

  \begin{subfigure}{0.9\columnwidth}
    \includegraphics[width=\linewidth]{data/CoverageByBenchmark30.pdf}
    \caption{Coverage results achieved in the competition with \SI{30}{\second}.}
    \label{fig:results30}
  \end{subfigure}

  \begin{subfigure}{0.9\columnwidth}
    \includegraphics[width=\linewidth]{data/CoverageByBenchmark120.pdf}
    \caption{Coverage results achieved in the competition with \SI{120}{\second}.}
    \label{fig:results120}
  \end{subfigure}

  \caption{Competition results achieved by \EVOSUITE summarised by projects from which the classes under test.}
  \label{fig:figures}
\end{figure}

With an overall score of \score, \EVOSUITE achieved the highest score of all
tools in the competition. As described in the competition
report~\cite{SBST-toolcomp22}, the score is the weighted sum between the
rankings for coverage and understandability.

Figure~\ref{fig:results30} summarises the results of \EVOSUITE in terms of the
mean coverage for the \cuts classes used in the competition for the \budgetShort search budget; Figure~\ref{fig:results120} shows the results for the \budgetLong search budget. The coverage
increased from the \budgetShort to the \budgetLong search budget (mean line
coverage of \avgLinesCoverageRatioShort vs. \avgLinesCoverageRatioLong, respectively).

\EVOSUITE failed to generate any tests in \numTestGenFailedShort cases with a
budget of \budgetShort, and in \numTestGenFailedLong cases with a budget of
\budgetLong. However, we found no crashes of \EVOSUITE itself (e.g., exceptions
thrown by \EVOSUITE), but in all cases where no tests were generated the
\EVOSUITE process had been killed by the competition setup, suggesting that
\EVOSUITE was using more time than allocated.

While the results for line coverage and branch coverage are similar, the
mutation scores are substantially lower. The mutation scores on the \Threeten
classes are highest compared to the other projects from which classes were taken.

@@

\begin{figure}
  \includegraphics[width=0.9\columnwidth]{./data/understandability}
  \caption{Distribution of test case understandability, ranked from 1 (best) to 5 (worst), per project.}
  \label{fig:readability}
\end{figure}

>>>>

\author{%
  \IEEEauthorblockN{Sebastian Schweikl}
  \IEEEauthorblockA{%
    \textit{University of Passau} \\
    Passau, Germany \\
    email address or ORCID
  }
  \and
  \IEEEauthorblockN{Gordon Fraser}
  \IEEEauthorblockA{%
    \textit{University of Passau} \\
    Passau, Germany \\
    email address or ORCID
  }
  \and
  \IEEEauthorblockN{Andrea Arcuri}
  \IEEEauthorblockA{%
    \textit{Kristiania University College and}\\ \textit{Oslo Metropolitan University} \\
    Oslo, Norway \\
    email address or ORCID
  }
}

@@

%-------------------------------------------------------------------------
\section{Introduction}
%
For the last 10 years, the annual unit test generation competition has
evaluated progress on unit test generation tools using a benchmark of Java
classes, on which different tools are applied and compared. In the 2023 edition
of the competition, five tools were applied on a set of \cuts classes. Details
about the procedure of the competition, the technical framework, and the
benchmark classes can be found in the competition
report~\cite{SBFT-toolcomp23}. \EVOSUITE achieved an overall score of \score,
which was the highest among the competing and baseline tools.

@@

%-------------------------------------------------------------------------
\section{Competition Setup}\label{sec:setup}

@@

  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\linewidth]{data/CoverageByBenchmark30.pdf}
    \caption{Results achieved in the competition with a budget of \budgetShort}
    \label{fig:results30}
  \end{subfigure}

  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\linewidth]{data/CoverageByBenchmark120.pdf}
    \caption{Results achieved in the competition with a budget of \budgetLong}
    \label{fig:results120}
  \end{subfigure}

  \caption{Coverage results achieved by \EVOSUITE per each of the 5~projects
    used in the competition}
  \label{fig:figures}
\end{figure}

With an overall score of \score \EVOSUITE was the highest ranking tool
(rank \rank) in the competition. The score is computed as the weighted
sum between the rankings for coverage (rank \rankCoverage) and understandability
(rank \rankUnderstandability). We refer to the competition report~\cite{SBFT-toolcomp23}
for more details.

The coverage \EVOSUITE achieved on the \cuts classes distributed across the \projects
projects used in the competition is illustrated in Figure~\ref{fig:results30} for a search
budget of \budgetShort, and in Figure~\ref{fig:results120} for a budget of \budgetLong.
The median line and branch coverage for the \budgetShort budget is
\medLinesCoverageRatioShort and \medConditionsCoverageRatioShort, and
increases to \medLinesCoverageRatioLong and \medConditionsCoverageRatioLong
for the \budgetLong budget. The median mutation coverage is \SI{0}{\percent} in
both cases, and equal to all the other tools used in the competition.

As stated in the competition report~\cite{SBFT-toolcomp23} \EVOSUITE is the
only tool for which the median number of generated tests \emph{decreases}
from \num{35} for the \budgetShort budget to \num{23.5} for the \budgetLong budget.
As stated before, \EVOSUITE tries to apply additional post-processing steps to remove
redundant tests. However, in case of the \budgetShort budget most time is spent on test
generation and only little time remains for minimisation.

% While the results for line coverage and branch coverage are similar, the
% mutation scores are substantially lower. The mutation scores on the \Threeten
% classes are highest compared to the other projects from which classes were taken.

% https://github.com/JUnitContest/JUGE/blob/master/benchmarktool/src/main/java/sbst/benchmark/Main.java#L160
In \numTestGenFailedShort cases \EVOSUITE failed to generate any tests with a
budget of \budgetShort. However, this might have been caused by problems in the
infrastructure\footnote{https://github.com/JUnitContest/JUGE/}
of the competition as we found no crashes or error messages
of \EVOSUITE itself. Instead, the log files contained the error message
``Error: null'' triggered by line~160 in the \texttt{main()} method of
the \texttt{sbst.benchmark.Main} class. Here, \EVOSUITE is invoked with an
\texttt{IBenchmarkTask} object as input which seems to have not been properly
initialised.
%
The same error also ocurred in 13 of \numTestGenFailedLong
cases with a budget of \budgetLong. In the remaining 4 cases, \EVOSUITE crashed
with an \texttt{OutOfMemoryError}. % while generating or postprocessing tests.

% threeten-extra-99 (2×)
% Test generation aborted
% Out of Memory Error GH overhead limit exceeded

% collections-10
% Crash
% java.lang.OutOfMemoryError: Java heap space during test suite minimisation

% ta4j-79
% java.lang.OutOfMemoryError: GC overhead limit exceeded while post-processing tests

@@

As a general trend, participants seem to value expressive names for test cases
variables, separation of concerns (i.e., unrelated functionality is )
and meaningful assertions.

shorter tests

\begin{figure}
  \includegraphics[width=\columnwidth]{./data/understandability}
  \caption{Distribution of test case understandability, ranked from 1 (best) to 5 (worst), per project}
  \label{fig:readability}
\end{figure}
